Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-22 Outputs Folder/paper_final.qmd
Fixed some grammatical issues in Paper

# Dataset Explanation
In this report, We used the programming language R [@citeR] and library packages include `AER`[@AER], `future`[@future], `gircreds`[@gitcreds], `knitr`[@knitr], `lintr`[@lintr], `renv`[@renv], `reprex`[@reprex], `styler`[@styler], `tictoc`[@tictoc], `tidyverse`[@tidyverse], `tinytex`[@tinytex], and `usethis`[@usethis] to conduct in-depth analysis from multiple aspects. Prior to analysis, we resolved missing data and extracted relevant temporal components for annual trend analysis.

@@

```
\break
## Potential Relationship between CPI and Number of Infractions
CPI is an economic indicator that measures changes in the inflation rate or cost of living in a country or region [@goldberg2010sensitivity]. The relevant data for this CPI comes from Toronto's Dashboard Key Indicators data set published by the City of Toronto @opendatatoronto. We generated two line charts [@fig-trend_comparison_of_cpi_and_infractions], showing the CPI trend and the Infraction number trend respectively. Observation shows that when CPI decreases, corporate hygiene violations will increase. Although there may not be a direct causal relationship between the two, their trends may be affected by similar external factors. For example, a decline in CPI is usually a sign of a recession, which indicates that Toronto residents will potentially have more difficulties financially; therefore, businesses will spend less money on maintaining food safety conditions in order to stabilize the economic situation.

>>>>

# Dataset Explanation
In this report, we used the programming language R [@citeR] and library packages include `AER`[@AER], `future`[@future], `gircreds`[@gitcreds], `knitr`[@knitr], `lintr`[@lintr], `renv`[@renv], `reprex`[@reprex], `styler`[@styler], `tictoc`[@tictoc], `tidyverse`[@tidyverse], `tinytex`[@tinytex], and `usethis`[@usethis] to conduct in-depth analysis from multiple aspects. Prior to analysis, we resolved missing data and extracted relevant temporal components for annual trend analysis.

@@

```
\break
## Potential Relationship between CPI and Number of Infractions
CPI is an economic indicator that measures changes in the inflation rate or cost of living in a country or region [@goldberg2010sensitivity]. In the early days of writing this report, the AI language model ChatGPT 4 [@openai2023chatgpt4] provided the author with inspiration for relevant economic indicators; the author finally selected CPI as a suitable indicator. The relevant data for this CPI comes from Toronto's Dashboard Key Indicators data set published by the City of Toronto @opendatatoronto. We generated two line charts [@fig-trend_comparison_of_cpi_and_infractions], showing the CPI trend and the infraction number trend respectively. Observation shows that when CPI decreases, corporate hygiene violations will increase. Although there may not be a direct causal relationship between the two, their trends may be affected by similar external factors. For example, a decline in CPI is usually a sign of a recession, which indicates that Toronto residents will potentially have more difficulties financially; therefore, businesses will spend less money on maintaining food safety conditions in order to stabilize the economic situation.
